DOpElib:\\ Differential Equations and Optimization Environment

### 2014-01-02 Examples/Documentation/introduction.tex
Added only_recent behavior to the StateVector

\subsection{Vectors}
\begin{itemize}
\item \texttt{include/statevector.h} This stores all dofs in space and time for the state 
  variable $u$. It is possible to select whether all this should be kept in memory or 
  or unused parts can be written to the hard disk.
\item \texttt{include/controlvector.h} This stores all dofs in space and time for the 
  control variable $q$. At present no time dependence is implemented.
\item \texttt{include/constraintvector.h} This stores all dofs in space and time for the 
  non PDE constraints (and corresponding multipliers). 
  At present no time dependence is implemented.
\end{itemize}
\begin{remark}
\label{remark_state_behavior}
We notice that the behavior of the statevector can be chosen as 
\texttt{fullmem} or \texttt{store\underline{ }on\underline{ }disc}. In the
first state, the RAM memory of the computer is used. In the second state,
all vectors are written on disc, to avoid the RAM. This might take some 
time at the beginning of a new executing program (cleary depending 
on the number of spatial and temporal unknowns and the capabilities of your 
local machine). In addition, if the program aborts abnormally in the 
using \texttt{store\underline{ }on\underline{ }disc} behavior, please make 
sure to remove manually the \texttt{tmp\underline{ }state} folder in your 
\texttt{Results} folder. 
\end{remark}

>>>>

\subsection{Vectors}
\begin{itemize}
\item \texttt{include/statevector.h} This stores all dofs in space and time for the state 
  variable $u$. It is possible to select whether all this should be kept in memory or 
  or unused parts can be written to the hard disk.
\item \texttt{include/controlvector.h} This stores all dofs in space and time for the 
  control variable $q$. At present no time dependence is implemented.
\item \texttt{include/constraintvector.h} This stores all dofs in space and time for the 
  non PDE constraints (and corresponding multipliers). 
  At present no time dependence is implemented.
\end{itemize}
\begin{remark}
\label{remark_state_behavior}
We notice that the behavior of the statevector can be chosen as 
\texttt{fullmem}, \texttt{only_recent}, or 
\texttt{store\underline{ }on\underline{ }disc}. In the
first state, the RAM memory of the computer is used. In the second state,
only the spatial vectors at the current time step (and the preious one)
are stored. This reduces memory requirements, but also prohibits access to the
whole space-time trajectory after the computation.
In the third state,
all vectors are written on disc, to avoid the RAM. This might take some 
time at the beginning of a new executing program (cleary depending 
on the number of spatial and temporal unknowns and the capabilities of your 
local machine). In addition, if the program aborts abnormally in the 
using \texttt{store\underline{ }on\underline{ }disc} behavior, please make 
sure to remove manually the \texttt{tmp\underline{ }state} folder in your 
\texttt{Results} folder. 
\end{remark}

### 2014-01-02 Examples/PDE/InstatPDE/Example2/content.tex
Added only_recent behavior to the StateVector

>>>>

Further, this example shows, how to change the vector behavior, from 
our default option \texttt{fullmem}, where the whole vector is stored in 
the computers main memory. Here, we are only interested in calculating the 
solution once, hence two vectors, one for the current time point and one for the
previous one are sufficient. Hence we choose the option 
\texttt{only_recent} so that we don't have to reserve unneccessary memory.
If we need to store the whole trajectory for some reason another option is available 
to circumvent the restrictions due to the size of the main memory, it will be 
described in Example~\ref{PDE_Instat_Black_Scholes}.

### 2014-01-02 Examples/PDE/InstatPDE/Example3/content.tex
typo
Added only_recent behavior to the StateVector

This behavior is particularly useful, if many time steps are taken; so that the 
whole set of unknowns can no longer be stored in main memory. Note that all vectors 
will allocate the required memory when the vector is reinitialized to a new size.
Hence, for large vectors this may need some time.

To avoid multiple programs accessing the same files on the hard drive, a 
\texttt{lock} file is initialized. Under normal conditions, this will be deleted 
once the program terminates. However, should the program exit exceptionally, the 
lock file will still exist. Calling the program in this case will produce an 
exception, with the following text:
\begin{verbatim}
Warning: During execution of `StateVector<VECTOR>::StateVector` 
         the following Problem occurred!
The directory Results/tmp_state/ is propaply already in use.
\end{verbatim}
To resolve the issue, you have to delete the named directory with the 
temporary storage files manually.

>>>>

This behavior is particularly useful, if many time steps are taken; so that the 
whole set of unknowns can no longer be stored in main memory, but access to all
parts of the solution is required after the solution process and thus the 
option \texttt{only_recent} used in Example~\ref{PDE_Instat_FSI} is not sufficient.
Note that all vectors 
will allocate the required memory when the vector is reinitialized to a new size.
Hence, for large vectors this may need some time.

To avoid multiple programs accessing the same files on the hard drive, a 
\texttt{lock} file is initialized. Under normal conditions, this will be deleted 
once the program terminates. However, should the program exit exceptionally, the 
lock file will still exist. Calling the program in this case will produce an 
exception, with the following text:
\begin{verbatim}
Warning: During execution of `StateVector<VECTOR>::StateVector` 
         the following Problem occurred!
The directory Results/tmp_state/ is probably already in use.
\end{verbatim}
To resolve the issue, you have to delete the named directory with the 
temporary storage files manually.
